Model to study co-evolution of trade an culture

### 2015-03-27 article.tex

\subsection{Trading Model}\label{sec:trade}

@@

@@

\section{RESULTS}

>>>>

%%A integrer
Knowing that and following \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}, we think that in our model those prices will behave exactly like any other cultural trait, and that the different version of prices for each good will be found in the population in proportion that follow a power law.

It's indeed what we observe. In the first experiment, in order to compare our result with those of the literature, we use only one price. We check for some of the same $\mu$ value used in \cite{bentley_specialisation_2005,mesoudi_random_2009} that the distribution of the number of variants are the same.

\subsection{Trading Model}\label{sec:trade}
%%à integrer
In the previous experiment the estimate price of good have no impact on the agents choices and behaviors. In a real economical system it's not the case. In order to approximate such a process and to see how our framework could handle economical mechanism we introduce a new cultural transmission mechanism.

This time agent will not copying randomly the vector of price from one random individual but they will choose among the agent that produce the same good those that seem the most successful. In practice, a fixed proportion of the less successful agents will copy the prices of the more successful agent.

Meanwhile time the innovation mechanism used in the experiment  we follow in the previous section seems not  an adequate economical mechanism. While in a cultural point a view an innovation could be anything new in you space innovation, it's seem little probable than a price will be change to something totally new.

That why we  introduce a new innovation mechanism which will also occur with a probability of $\mu$ but this time, instead of set a totally new price, it will modify the previous price by adding or subtract to it a small amount randomly choose between $0 .. \beta$.

@@

%%A integrer
To express this idea of success we define a score that is maximum when you manage to have exactly the needed amount for each good. If you exchange too much or too few of one of the good your score will decreased. The score is computed in such a way that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value won't help you to increase your score).

@@

\section{RESULTS}
\subsection{Random cultural transmission and random innovation process}
\subsubsection{One trait}

That is what we can see in the figure \ref{fig:allMutation}.

Each curves on the figures show the mean for 100 runs. In our experiment one has to take in account that agents modifies their prices or exchange their price only every ten steps. Between, they exchange goods given their own prices. Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}, for $\mu$ the innovation rate $\in {.004,.008,.016,.064}$ and for 250 and 500 agents.

\simon{reference to the R package and the theoreticla ref in the Rpackage?}
Those distribution exhibit power law like attribute and we can fit them. The result of the alpha fitted with are in the table \ref{tab:mualpha}. The alpha values represent the mean of the fitted alpha for each run computed using RPACKAGE with the standard deviation associated with each mean.
\begin{figure}[hbp]
	\begin{center}
		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
	\end{center}
	\caption{rand()\%RAND\_MAX}
	\label{fig:allMutation}
\end{figure}

\begin{table}
	\centering
	\begin{tabular}{cc}
		\begin{tabular}{l|cc}
			$\mu$ & $\alpha$ & SD\\\hline
			0.004&1.541193&0.031384174\\
			0.008&1.549726&0.021953251\\
			0.016&1.568096&0.017025456\\
			0.064&1.651690&0.006538209\\

		\end{tabular}
		&
		\begin{tabular}{l|cc}
			$\mu$ & $\alpha$ & SD\\\hline
			0.004&1.539710&0.022515901\\
			0.008&1.557460&0.017805810\\
			0.016&1.570036&0.004412181\\
			0.064&1.651521&0.009988488\\
		\end{tabular}\\
		(a) & (b)
	\end{tabular}
	\caption{Mean \& SD are done with 100 run for each with 250 agent for (a) and 500 for (b) }
	\label{tab:mualpha}
\end{table}

\subsubsection{Multiple traits co-evolving randomly}
\simon{ this part could be resumed to one phrase saying that nothing change and that we check it without showing any result moreover}
As our aims is to study the evolution of an economy where people exchange different goods, we have checked if the previous results are the same when the agents own not just one price for one good but a vector of price associated to each good available in the environment. And every thing is OKAY

%\begin{table}
%	\centering
%		\begin{tabular}{l|cccc}
%			  & g=1  & g= 2 & g=3 & g=4 \\\hline
%			$\alpha$&\\
%			sd \\
%		\end{tabular}
%	\caption{alpha is the mean alpha between each good for 100 runs }
%	\label{tab:alphagoods}
%\end{table}

\subsection{ Economical  process}

In order to study the impact of the introduction of those new mechanism  we summarize it in the table~\ref{tab:exp}. 
\begin{table}
	\centering
	\begin{tabular}{l|c|c}
		& Rand & Eco \\\hline
		$\mu$ &A & B \\
		$\mu +\alpha$ & C & D \\
	\end{tabular}
	\caption{Experimental Setup}
	\label{tab:exp}
\end{table}

The following  experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population. All the next experiments are run during 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
